Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-05 paper.tex
changes to intro

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{epsfig,psfrag,txfonts,xspace}
\usepackage[normalem]{ulem}
\usepackage{graphicx,color}
\usepackage{natbib}
\usepackage{amsfonts,amsbsy,amssymb}

% --- journals --- %
\newcommand{\aap}{A{\&}A}
\newcommand{\aaps}{A{\&}AS}
\newcommand{\aapr}{AAPR}
\newcommand{\aj}{AJ}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\apjs}{ApJS}
\newcommand{\apss}{Ap{\&}SS}
\newcommand{\araa}{ARA{\&}A}
\newcommand{\memsai}{{Mem.~Soc.~Astron.~Italiana}}
\newcommand{\mnras}{MNRAS}
\newcommand{\ssr}{SSRv}
\newcommand{\physrep}{Phys.~Rep.}
\newcommand{\jcomp}{J.~Comput.~Phys.}
\newcommand{\jgr}{JGR}
\newcommand{\grl}{GRL}
\newcommand{\nat}{Nature}
\newcommand{\Mstream}{{\it M-streaming}\xspace}
\newcommand{\Mflatturb}{{\it M-turbulence}\xspace}
\newcommand{\Mprimary}{{\it M-primaries}\xspace}

% --- macros --- %
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\mu G}
\newcommand{\RH}{R_\rmn{RH}}

@@

\begin{abstract}
  About one third of X-ray-luminous clusters show smooth, unpolarized
  radio emission on $\sim$Mpc scales, known as giant radio halos. One
  promising model for radio halos is Fermi II acceleration of seed
  relativistic electrons by turbulence in the intracluster medium
  (ICM); Coulomb losses prohibit acceleration from the thermal
  pool. However, the origin of seed electrons has never been fully
  explored. Here, we integrate the Fokker-Planck equation of the
  cosmic ray (CR) electron and proton distributions in cosmological
  simulations of cluster formation. For standard assumptions,
  structure formation shocks lead to a seed electron population which
  produces too centrally concentrated radio emission. Instead, we
  present three plausible scenarios for the seed CRs that each
  can reproduce the spatially flat radio emission observed in the Coma
  cluster. (1) The CR proton to electron acceleration efficiency
  $K_\rmn{ep} \sim 0.1$ is assumed to be larger than in our Galaxy
  ($K_\rmn{ep} \sim 10^{-2}$), due to the magnetic geometry at the
  shock. The resulting primary electrons dominate the radio emission,
  which is more extended in comparison to radio emission from
  secondary electrons that result from hadronic CR interactions in the
  ICM. (2) CR protons may stream at the Alfv{\'e}n speed to the
  cluster outskirts when the ICM is relatively quiescent. A spatially
  flat CR proton distribution develops and produces the required
  population of secondary seed electrons. (3) The ratio of injected
  turbulent energy density to thermal energy density increase
  significantly with radius, as seen in cosmological simulations. This
  generates a flat radio profile when CRs are reaccelerated even
  if the seed population of CRs is steep with radius. These competing
  non-trivial solutions provide incisive probes of non thermal
  processes in the high-$\beta$ ICM.
\end{abstract}

@@

% --- section: Introduction --- %
\section{Introduction}
About one third of X-ray-luminous clusters show smooth, unpolarized
radio emission on $\sim$Mpc scales, known as giant radio halos (RHs)
\citep{2014IJMPD..2330007B}. They appear only in disturbed, merging
clusters and the RH luminosity correlates with the X-ray luminosity
\citep{2001A&A...369..441G,2012A&ARv..20...54F} and the Compton
$y$-parameter \citep{2013A&A...554A.140P}. The RHs show that CRs and
magnetic fields permeate a large volume fraction of the intra-cluster
medium (ICM). The dominant CR source, given the smoothness and
enormous extent of RHs, is thought to be structure formation shocks
\citep{miniati01,pfrommer08}. At the same time, plasma processes, the
origin of magnetic fields and particle acceleration in a turbulent,
high-$\beta$ plasma like the ICM are not well understood. Radio halos
thus provide an incisive probe of non-thermal processes in the ICM.

@@

However, there is a salient piece missing in the turbulent
reacceleration model. It relies heavily on the assumption of an
abundant, volume-filling population of seed suprathermal electrons;
direct Fermi II acceleration from the thermal pool is precluded by
strong Coulomb losses
\citep{2008ApJ...682..175P,2012ApJ...759..113C}. These seeds are
presumed to be either fossil CR electrons (CRes) accelerated by
diffusive shock acceleration (DSA) during structure formation
\citep{1999ApJ...520..529S}, or secondaries injected by hadronic
interaction of CR protons (CRps) with thermal protons
\citep{brunetti11}. While analytic estimates have been made, there has
been no ab initio demonstration that structure formation can lead to
the required abundance of seed electrons with the correct spatial and
spectral characteristics. This is a non-trivial requirement: Coulomb
cooling in dense cluster cores is severe, and DSA fossil electrons may
not survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
\AP{the left panel of} Fig.~\ref{fig:Edens} we show that such a
distribution is not predicted by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}.
\begin{figure*}
  \includegraphics[width=1.0\columnwidth]{figures/fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
  \includegraphics[width=1.0\columnwidth]{figures/turb_profile_ratio_tot.eps}
  \caption{Left: spatial distribution of CRp energy density in the
    Coma cluster. The red dash-dotted line shows the required
    distribution of seed CRps that generate secondary electrons via
    p-p collisions required to reproduce Coma radio brightness
    observations after Fermi-II reacceleration \citep{brunetti12}. The
    blue solid line shows the distribution of fossil CRps found in
    cosmological simulations, which disagrees with the required
    profile. \AP{To better compare the two models in this figure, we
      normalize the required distribution of CRps by fixing the total
      CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
      energy, consistent with observations
      \citep{2014ApJ...787...18A,2012ApJ...757..123A}. Right: the
      ratio of turbulent-to-thermal energy densities (solid lines) and
      cumulative energies (dotted lines) in our three models. The
      energy densities are parametrized as $\epsilon_\rmn{turb}
      \propto \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
      normalized such that the total turbulent energy in compressible
      modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
      total thermal energy $E_\rmn{th}$ inside the radio halo
      ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
      the uncertainty in the cluster turbulence and are motivated by
      the cosmological simulation in
      \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}}
  \label{fig:Edens}
\end{figure*}

\CP{Could you add a comparison to Miniati's work here and discuss the
  right panel of figure 1 and table 1? Do we want to move the figure
  to a later section?}  Indeed, arriving at a seed population with the
required characteristics is highly constraining, and has the potential
to teach us much about the origin of CRps/CRes in clusters. \AP{For
  both the turbulence and magnetic fields we adopt stationary models,
  parameterized in terms of thermal quantities derived from our
  simulations.} In this paper we consider three new scenarios that
individually or combined can reproduce the observed radio profiles and
spectrum in the Coma cluster without violating gamma-ray constraints:
\begin{enumerate}
\item {\bf Model {\em M-primaries}.} If the acceleration efficiency of CRps is below
  about $0.1$~{\%} in weak (perpendicular) shocks and the ratio of injected
  electrons-to-protons $K_{\rmn{ep}} \sim 0.1$, this yields a dominant primary
  population with a flat spatial distribution, since primaries have a weaker
  density dependence than secondaries.
\item {\bf Model {\em M-streaming}.} Here, we account for streaming CRps that
  produce flat distributions of CRps in the ICM
  \citep{ensslin11,wiener13,2014MNRAS.438..124Z}, which also flattens the
  secondary electron distribution.
\item {\bf Model {\em M-turbulence}.} Here, we adopt a significantly spatially
  flatter turbulent profile than what was adopted in \citet{brunetti12},
  but where seed CRps follow the steep profile that is suggested by
  structure formation simulations.
\end{enumerate}

@@

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency (see \cite{pinzke13} for more
discussion). However, as recent PIC simulations have shown, this is
likely very different at weak shocks, with electrons efficiently
accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. In this work we use a simple test-particle model for the
CRp acceleration, where we adopt a fit to Monte Carlo simulations of
the thermal leakage process that relates the momentum of injected
protons to the thermal energy of the shocked plasma \citep{kang11}. We
set an upper limit on the ratio of accelerated proton-to-dissipated
energy in the downstream of strong shocks that varies from 1-10\%,
depending on the adopted model (for more details, see Section
\ref{sec:results}). In order not to violate energy conservation with a
fixed limit for the acceleration efficiency, we steepen the spectral
index of the accelerated CRps at the limit \citep{pinzke13}, which
mimics the non-linear CR modification of the shock
\citep{ellison00}. For weak shocks the efficiency is a factor 10-100
lower and well below the limit. Some observations of radio relics
suggest high values of $K_{\rmn{ep}}$, due to the absence of gamma-ray
emission, which probes the CRp population
\citep{2014MNRAS.437.2291V}. This suggests primary CRes as a viable
alternative scenario to secondary CRes as seeds for the giant RHs. In
our {\em M-primaries} scenario, the injected distribution of CRes is
derived in the same way as for the CRps. Once they have been
accelerated to relativistic energies, injected electrons and protons
are indistinguishable. We therefore assume that CRp and CRe have the
same distribution function $f_\rmn{CRe}(p) = K_\rmn{ep}
f_\rmn{CRp}(p)$, with a different normalization (due to differing
acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[viable for primarily
perpendicular shocks]{2014ApJ...794..153G}. While this
appears to contradict the radial bias of magnetic fields in the bulk
of the ICM as suggested by observations \citep{2010NatPh...6..520P}
and cluster simulations \citep{2011ApJ...740...81R}, it does not
necessarily apply to the accretion shock regions, which show a field
geometry with a net perpendicular bias with respect to the shock
normal---at least for giant radio relics \citep{2010Sci...330..347V}.

\subsection{Cosmic ray transport}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations; because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaniously produces flat CRp profiles. \sout{We assume that CRs cannot
stream significantly past perpendicular $B$-fields at the accretion
shock, so that the total number of CRs is conserved within the galaxy
cluster during the streaming process.}

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm C} 
+ \frac{p}{3}\left(\vec{\nabla}\cdot \vec{\upsilon}\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\vec{\nabla}\cdot \vec{\upsilon}\right) f_{\rmn{e}}(p,t)
- \vec{\nabla}\cdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\vec{\upsilon}\cdot \vec{\nabla}$ is the Lagrangian derivative,
$\vec{\upsilon}$ is the gas velocity, $|dp/dt|$ represents radiative
(r) and Coulomb (C) losses, $D_{pp}$ is the momentum space diffusion
coefficient, and $Q_{\rmn{e}}$ denotes the injection rate of primary
and secondary electrons in the ICM. The $\vec{\nabla}\cdot
\vec{\upsilon}$ terms represent adiabatic gains and losses \AP{and the
  $\vec{\nabla}\cdot \vec{F}_\rmn{stream}$ terms represent
  super-Alfv{\'e}nic CR streaming. For details about $F_\rmn{stream}$
  please see \citet{wiener13}.} During post-processing of our
Coma-like cluster simulation, we solve the Fokker-Planck equation over
a redshift interval from $z=5$ to 0. The simulated cluster undergoes a
major merger over the last 1-2~Gyrs that \AP{is thought to inject
  large turbulent eddies. Following \citet{brunetti07,brunetti11}
  \citep[see also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we
  assume that about one Gyr after core passage the fields have decayed
  down to the smallest scales where reacceleration is most efficient
  ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on shortly
  after. Note that the exact decay time of the turbulens is of minor
  importance, since the thermal and CR quantities are very similar a
  few 100 Myrs before and after $z=0$ where we have chosen to evaluate
  the simulations.}  \sout{injects large turbulent eddies. After about
  1~Gyr those have decayed down to the scale needed to reaccelerate
  particles.} This delay naturally explains why giant radio halos are
only seen in a fraction of all merging clusters. In all our
calculations we assume that turbulent reacceleration efficiently
accelerates particles for $\tau_D\sim650$~Myrs (which is roughly the
cascade time on which turbulence is damped) and that during this
turbulent phase CR streaming and spatial diffusion can be
neglected. In our \Mstream model, CR streaming and diffusion are
incorporated separately during kinematically quiescent times that
precede the merger. As a result, flat CRp profiles are produced on
relatively short timescales ($\sim 0.1-0.5$ Gyr). \AP{This allows us
  to implicitly solve for CR streaming in our calculations, where we
  adopt a toy model that enforce a flat CRp profile at all quiescent
  times \citep{wiener13}. We assume that CRs cannot stream
  significantly past perpendicular $B$-fields at the accretion shock,
  so that the total number of CRs is conserved within the virial
  radius during the streaming process. Finally, since streaming is
  much more efficient for the CRps, we can ignore this effect for the
  CRes.}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage{txfonts}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx,color}	% Including figure files
%\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{amsbsy}
\usepackage[normalem]{ulem}
\usepackage{mathrsfs,bm,xspace}
\newcommand{\bcdot}{\ensuremath{%
  \mathchoice%
   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}}%
   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}%        
   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%  
   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%
}

% --- macros --- %
\newcommand{\Mstream}{{\it M-streaming}\xspace}
\newcommand{\Mflatturb}{{\it M-turbulence}\xspace}
\newcommand{\Mprimary}{{\it M-primaries}\xspace}

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\mu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}

@@

\begin{abstract}
  About one third of X-ray-luminous clusters show smooth, unpolarized
  radio emission on $\sim$Mpc scales, known as giant radio halos. One
  promising model for radio halos is Fermi II acceleration of seed
  relativistic electrons by compressible turbulence in the
  intracluster medium (ICM); Coulomb losses prohibit acceleration from
  the thermal pool. However, the origin of seed electrons has never
  been fully explored. Here, we integrate the Fokker-Planck equation
  of the cosmic ray (CR) electron and proton distributions in
  cosmological simulations of cluster formation. For standard
  assumptions, structure formation shocks lead to a seed electron
  population which produces too centrally concentrated radio
  emission. Instead, we present three plausible scenarios for the seed
  CRs that each can reproduce the spatially flat radio emission
  observed in the Coma cluster. (1) The CR proton-to-electron
  acceleration efficiency $K_\rmn{ep} \sim 0.1$ is assumed to be
  larger than in our Galaxy ($K_\rmn{ep} \sim 10^{-2}$), due to the
  magnetic geometry at the shock. The resulting primary electrons
  dominate the radio emission, which is more extended in comparison to
  radio emission from secondary electrons that result from hadronic CR
  interactions in the ICM. (2) CR protons may stream at the Alfv{\'e}n
  speed to the cluster outskirts when the ICM is relatively
  quiescent. A spatially flat CR proton distribution develops and
  produces the required population of secondary seed electrons. (3)
  The ratio of injected turbulent-to-thermal energy density increases
  significantly with radius, as seen in cosmological simulations. This
  generates a flat radio profile when CRs are reaccelerated even if
  the seed population of CRs is steep with radius. These competing
  non-trivial solutions provide incisive probes of non thermal
  processes in the high-$\beta$ ICM.
\end{abstract}

@@

% --- section: Introduction --- %
\section{Introduction}
About one third of X-ray-luminous clusters show smooth, unpolarized
radio emission on $\sim$Mpc scales, known as giant radio halos (RHs)
\citep{2014IJMPD..2330007B}. They appear only in disturbed, merging
clusters and the RH luminosity correlates with the X-ray luminosity
\citep{2001A&A...369..441G,2012A&ARv..20...54F} and the Compton
$y$-parameter \citep{2012MNRAS.421L.112B,2013A&A...554A.140P}. The RHs
show that CR electrons and magnetic fields permeate a large volume
fraction of the intra-cluster medium (ICM). The dominant CR source,
given the smoothness and enormous extent of RHs, is thought to be
structure formation shocks \citep{miniati01,pfrommer08}. At the same
time, plasma processes, the origin of magnetic fields and particle
acceleration in a turbulent, high-$\beta$ plasma like the ICM are not
well understood. Radio halos thus provide an incisive probe of
non-thermal processes in the ICM.

@@

However, there is a salient piece missing in the turbulent
reacceleration model. It relies heavily on the assumption of an
abundant, volume-filling population of seed suprathermal electrons;
direct Fermi II acceleration from the thermal pool is precluded by
strong Coulomb losses
\citep{2008ApJ...682..175P,2012ApJ...759..113C}. These seeds are
presumed to be either fossil CR electrons (CRes) accelerated by
diffusive shock acceleration (DSA) during structure formation
\citep{1999ApJ...520..529S}, or secondaries injected by hadronic
interaction of CR protons (CRps) with thermal protons
\citep{brunetti11}. While analytic estimates have been made, there has
been no ab initio demonstration that structure formation can lead to
the required abundance of seed electrons with the correct spatial and
spectral characteristics. This is a non-trivial requirement: Coulomb
cooling in dense cluster cores is severe, and DSA fossil electrons may
not survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
\AP{the left panel of} Fig.~\ref{fig:Edens} we show that such a
distribution is not predicted by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}. \CP{Explain Fig 1: why is
  simulated profile steep? transport, secondaries, \ldots}

\begin{figure*}
  \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
  \caption{Left: spatial distribution of CRp energy density in the
    Coma cluster. The red dash-dotted line shows the required
    distribution of seed CRps that generate secondary electrons via
    p-p collisions required to reproduce Coma radio brightness
    observations after Fermi-II reacceleration \citep{brunetti12}. The
    blue solid line shows the distribution of fossil CRps found in
    cosmological simulations, which disagrees with the required
    profile. \AP{To better compare the two models in this figure, we
      normalize the required distribution of CRps by fixing the total
      CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
      energy, consistent with observations
      \citep{2014ApJ...787...18A,2012ApJ...757..123A}. Right: the
      ratio of turbulent-to-thermal energy densities (solid lines) and
      cumulative energies (dotted lines) in our three models. The
      energy densities are parametrized as $\epsilon_\rmn{turb}
      \propto \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
      normalized such that the total turbulent energy in compressible
      modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
      total thermal energy $E_\rmn{th}$ inside the radio halo
      ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
      the uncertainty in the cluster turbulence and are motivated by
      the cosmological simulation in
      \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}}
  \label{fig:Edens}
\end{figure*}

Indeed, arriving at a seed population with the required
characteristics is highly constraining, and has the potential to teach
us much about the origin of CRps/CRes in clusters.  \CP{We use our
  simuations to generate distribution function of seed population,
  resolve injection and loss processes for CRs and integrate the
  Fokker-Planck equation along Lagrangian particle trajectories to
  obtain a momentum spectrum of CRs. However, we assume a simplified
  turbulent model. So our approach is orthogonal (and complementary)
  to e.g. Miniati 2015.}  \AP{For both the turbulence and magnetic
  fields we adopt stationary models, parameterized in terms of thermal
  quantities derived from our simulations.}

In this paper we consider three new scenarios that
individually or combined can reproduce the observed radio profiles and
spectrum in the Coma cluster without violating gamma-ray constraints:
\begin{enumerate}
\item {\bf Model {\em M-primaries}.} If the acceleration efficiency of CRps is below
  about $0.1$~{\%} in weak (perpendicular) shocks and the ratio of injected
  electrons-to-protons $K_{\rmn{ep}} \sim 0.1$, this yields a dominant primary
  population with a flat spatial distribution, since primaries have a weaker
  density dependence than secondaries.
\item {\bf Model {\em M-streaming}.} Here, we account for streaming CRps that
  produce flat distributions of CRps in the ICM
  \citep{ensslin11,wiener13,2014MNRAS.438..124Z}, which also flattens the
  secondary electron distribution.
\item {\bf Model {\em M-turbulence}.} Here, we adopt a spatially
  flatter turbulent profile than what was adopted in \citet{brunetti12},
  but where seed CRps follow the steep profile that is suggested by
  structure formation simulations.
\end{enumerate}

@@

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency (see \cite{pinzke13} for more
discussion). However, as recent PIC simulations have shown, this is
likely very different at weak shocks, with electrons efficiently
accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. In this work we use a simple test-particle model for the
CRp acceleration, where we adopt a fit to Monte Carlo simulations of
the thermal leakage process that relates the momentum of injected
protons to the thermal energy of the shocked plasma \citep{kang11}. We
set an upper limit on the ratio of accelerated proton-to-dissipated
energy in the downstream of strong shocks that varies from 1-10\%,
depending on the adopted model (for more details, see Section
\ref{sec:results}). In order not to violate energy conservation with a
fixed limit for the acceleration efficiency, we steepen the spectral
index of the accelerated CRps at the limit \citep{pinzke13}, which
mimics the non-linear CR modification of the shock
\citep{ellison00}. For weak shocks the efficiency is a factor 10-100
lower and well below the limit. Some observations of radio relics
suggest high values of $K_{\rmn{ep}}$, due to the absence of gamma-ray
emission, which probes the CRp population
\citep{2014MNRAS.437.2291V}. This suggests primary CRes as a viable
alternative scenario to secondary CRes as seeds for the giant RHs. In
our {\em M-primaries} scenario, the injected distribution of CRes is
derived in the same way as for the CRps. Once they have been
accelerated to relativistic energies, injected electrons and protons
are indistinguishable. We therefore assume that CRp and CRe have the
same distribution function $f_\rmn{CRe}(p) = K_\rmn{ep}
f_\rmn{CRp}(p)$, with a different normalization (due to differing
acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is viable for
  primarily perpendicular shocks][]{2014ApJ...794..153G}. While this
appears to contradict the radial bias of magnetic fields in the bulk
of the ICM as suggested by observations \citep{2010NatPh...6..520P}
and cluster simulations \citep{2011ApJ...740...81R}, it does not
necessarily apply to the accretion shock regions, which show a field
geometry with a net perpendicular bias with respect to the shock
normal---at least for giant radio relics \citep{2010Sci...330..347V}.

\subsection{Cosmic ray transport}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations; because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
stream significantly past perpendicular $B$-fields at the accretion
shock, so that the total number of CRs is conserved within the galaxy
cluster during the streaming process.}

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm C} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses \AP{and the $\bnabla\bcdot
  \vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
  streaming. For details about $F_\rmn{stream}$ please see
  \citet{wiener13}.} During post-processing of our Coma-like cluster
simulation, we solve the Fokker-Planck equation over a redshift
interval from $z=5$ to 0. The simulated cluster undergoes a major
merger over the last 1-2~Gyrs that \AP{is thought to inject large
  turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
    also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
  about one Gyr after core passage the fields have decayed down to the
  smallest scales where reacceleration is most efficient ($D_{pp}\sim
  k_\rmn{cut}$) and the radio halo turns on shortly after. Note that
  the exact decay time of the turbulens is of minor importance, since
  the thermal and CR quantities are very similar a few 100 Myrs before
  and after $z=0$ where we have chosen to evaluate the simulations.}
\sout{injects large turbulent eddies. After about 1~Gyr those have
  decayed down to the scale needed to reaccelerate particles.} This
delay naturally explains why giant radio halos are only seen in a
fraction of all merging clusters. In all our calculations we assume
that turbulent reacceleration efficiently accelerates particles for
$\tau_D\sim650$~Myrs (which is roughly the cascade time on which
turbulence is damped) and that during this turbulent phase CR
streaming and spatial diffusion can be neglected. In our \Mstream
model, CR streaming and diffusion are incorporated separately during
kinematically quiescent times that precede the merger. As a result,
flat CRp profiles are produced on relatively short timescales ($\sim
0.1-0.5$ Gyr). \AP{This allows us to implicitly solve for CR streaming
  in our calculations, where we adopt a toy model that enforce a flat
  CRp profile at all quiescent times \citep{wiener13}. We assume that
  CRs cannot stream significantly past perpendicular $B$-fields at the
  accretion shock, so that the total number of CRs is conserved within
  the virial radius during the streaming process. Finally, since
  streaming is much more efficient for the CRps, we can ignore this
  effect for the CRes.}

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
{{d f_{\rmn{p}}(p,t)}\over{d t}} &=&
{{\partial }\over{\partial p}}
\left\{
f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm C}
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)\right.\right.
\nonumber\\
&-&\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{p}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock
accelerated CRps as a function of momentum $p$ and time $t$, and
$\tau_{\rm had}$ is the timescale of hadronic losses that produce
pions via CRp collisions with thermal protons of the ICM
\cite[e.g.][]{brunetti11}.
